\textbf{Manual Coding Handbook} \\[1cm] A New Indicator of Automation \\ Based on Patent Text Search

### 2015-05-19 manual_classification/manual_coding_handbook.tex
Automatically download files from Google Patents

\begin{frame}
\textcolor{beamer@blendedblue}{\textbf{Definition:}}

	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a physical machine, computer program, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start)
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency-enhancing machines
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\item parts of computers or of sofware that does not directly contribute to automation
			\end{itemize}			
	\end{itemize}
\vspace{0.6cm}
\textcolor{beamer@blendedblue}{\textbf{Our question to you:}}
	\begin{itemize}	
	\item Does the patent we will show you, \textit{even just in a loose sense}, describe an automat?
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{https://www.google.com/patents}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely), please try at the USPTO search interface.
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list (don't ask us why...).
	\end{itemize}
\end{frame}

@@

@@

@@

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What if I don't understand what the patent is about?}\\[0.1cm]
	No problem, just judge if you think this patent might have something to contribute to automation. If you're not sure \textit{beyond reasonable doubt} (to use such a legal term), please indicate this in the comment box.
	\end{itemize}
\end{frame}

>>>>

\begin{frame}\frametitle{Definition}
	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a physical machine, computer program, an algorithm, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start) and with a reasonable amount of completeness (so it should not be a minor part of a computer or machine even if that was what we think of as an automat).
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency-enhancing machines
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\item parts of machines (e.g. a tube) that does not automate or that is not a part of an automat
			\item parts of computers or of sofware that does not directly contribute to automation
			\item highly abstract algorithms (a potential application in automation should be recognizable)
			\end{itemize}			
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Our question to you}
\vspace{0.6cm}
	\begin{itemize}	
	\item Does the patent we will show you, \textit{even just in a loose sense}, describe an automat?
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{https://www.google.com/patents}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface.
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list (don't ask us why...).
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Example: automation patent (a clear case)}
\href{https://www.google.de/patents/US8857476}{\texttt{8857476 : Coinfusion apparatus }}
	\begin{itemize}	
	\item This machine independently ``mix[es] and adjust[s] medical agent such as anticancer drug". This avoids the need for humans exposing themselves to dangerous materials. This means that  ``a part or the entirety of the coinfusion processing can be performed automatically by [the invention]".
	\item We classify this as a manual machine.
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
\href{https://www.google.de/patents/US4323683}{\texttt{4323683: Process for making pyridinethione salts }}
	\begin{itemize}	
	\item This is a manufacturing method to make salts used against dandruff. It is for various reasons not an automation patent: it is not a device (but a production method), it is not clear if a machine or a human will produce it 
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What if I don't understand what the patent is about?}\\[0.1cm]
	No problem, just judge if you think this patent might have something to contribute to automation. If you're not sure \textit{beyond reasonable doubt} (to borrow such a legal term), please indicate this in the comment box.
	\end{itemize}
\end{frame}
